\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-27 paper.tex
Update on Overleaf.

\subsection{Representing Alternative States of the World}\label{alter}

@@

Complementing the spatial representation encapsulated in the scene graph, each
world also stores the world's \emph{timeline}. This data structure is shared and
synchronised amongst the clients in the same way as the scene graph.  Clients
can record and query both \emph{events} (duration-less states) and \emph{situations} in
the timeline, \ie states with a start time and a (possibly open-ended) end time.

%Importantly, the \uwds server automatically generates a snapshot of
%the scene graph whenever an event or situation is added to the timeline. The
%snapshot is associated to the event, which allows clients to effectively retrieve past
%states of the world. This capability is anticipated to be primarily used by \uwds clients
%performing action recognition.

@@

In the common case of one client performing a full update of a single world
(with $p$ nodes) at each time step, the complexity of propagating these changes across
the network would be $O(p \times m)$. Figure~\ref{fig|performances} shows
measured propagation time for one change across up to 20 cascading worlds.

@@

We are currently setting up this kind of network in the framework of the European project MuMMER where a Pepper robot is intended to handle interactive situations in a Mall in Finland. One of the situation is a guiding task where Pepper will help people to find their route by pointing them landmarks and explaining them how to reach a destination. The use of \uwds enables to get knowledge about what the customer sees (or has seen) or not and to handle the task accordingly. We plan also to be able to add information coming from the dialogue (e.g. if the customer says that he has seen a particular landmark that could consequently be added to his belief world). Moreover, we plan also to use alternative world ability given by \uwds (as explained in \ref{alter}) (e.g. to create a world where we put the customer in front of the desired shop )would be able to infer a possible world where the customer will be put in front of the desired shop to be able to explain him what he will see at destination.

@@

\subsubsection{Representation capabilities} as presented in
section~\ref{design}, the current version of \uwds allows to represent
\emph{objects}, \emph{abstract entities} like groups and \emph{perspectives}.
\emph{Fields} are also part of the \uwds design, but are not yet implemented.
Fields are commonly used to represent
continuously-valued spatial entities. Fields might or might not be spatially
bounded. Examples include the working space of a robot arm (spatially bounded),
the field of view of a camera (spatially bounded), proxemics (potentially
unbounded). We plan to represent fields in \uwds using the memory-efficient
octomaps~\cite{hornung2013octomap} or NDT-OM maps~\cite{saarinen20133d}.
Similarly to geometric data,these datastructures
will not be directly stored with the nodes (nodes will refer to them through 
handles), but unlike geometric data, they will not be treated as immutable
datasets by the server, permitting real-time updates.

>>>>

\subsection{Representing Alternative States of the World}

@@

Complementing the spatial representation encapsulated in the scene graph, each
world also stores the world's \emph{timeline}. This data structure is shared
and synchronised amongst the clients in the same way as the scene graph.
Clients can record both \emph{events} (duration-less states) and
\emph{situations} in the timeline, \ie states with a start time and a (possibly open-ended) end time.

Importantly, the \uwds server automatically generates a snapshot of
the scene graph whenever an event or situation is added to the timeline. The
snapshot is associated to the event, which allows clients to effectively retrieve past
states of the world. This capability is anticipated to be primarily used by \uwds clients
performing action recognition.

@@

In the common case of one client performing a full update of a single world
(with $p$ nodes) at each time step, the complexity of propagating these changes across
the network would be $O(p \times m)$. Figure~\ref{fig|performances} shows
measured propagation time for one change across 20 cascading worlds.

@@

We are currently setting up this kind of network in the framework of the European project MuMMER where a Pepper robot is intended to handle interactive situations in a Mall in Finland. One of the situation is a guiding task where Pepper will help people to find their route by pointing them landmarks and explaining them how to reach a destination. The use of \uwds enables to get knowledge about what the customer sees (or has seen) or not and to handle the task accordingly. We plan also to be able to add information coming from the dialogue (e.g. if the customer says that he has seen a particular landmark that could consequently be added to his belief world). Moreover, we plan also to use imaginary world (as explained in \ref{})would be able to infer a possible world where the customer will be put in front of the desired shop to be able to explain him what he will see at destination.

@@

\subsubsection{Representation capabilities} as presented in
section~\ref{design}, the current version of \uwds allows to represent
\emph{objects}, \emph{abstract entities} like groups and \emph{perspectives}.
\emph{Fields} are also part of the \uwds design, but are not yet implemented.
Fields are commonly used to represent
continuously-valued spatial entities. Fields might or might not be spatially
bounded. Examples include the working space of a robot arm (spatially bounded),
the field of view of a camera (spatially bounded), proxemics (potentially
unbounded). We plan to represent fields in \uwds using the memory-efficient
octomaps~\cite{hornung2013octomap}. Similarly to geometric data, octomaps
will not be directly stored with the nodes (nodes will refer to them through 
handles), but unlike geometric data, they will not be treated as immutable
datasets by the server, permitting real-time updates.
